---
output:
  word_document: default
  html_document: default
---
```{r libraries, include=FALSE}
library(tidyverse)
library(tidymodels)
```

```{r}
trucks = read_csv('trucks.csv')
```
Task 1:  
```{r task 1}
ggplot(trucks, aes(Distance, Speeding)) +
  geom_point()
```

There appears to be two natural clusters of drivers: 1 group driving less than 100 miles/day and 1 group driving more than 100 miles/day.  

Task 2:
```{r task 2}
kmeans_recipe = recipe(~ Distance + Speeding, trucks) 

trucks_dummy = kmeans_recipe %>% 
  step_scale(all_numeric()) %>%
  step_center(all_numeric()) 

trucks_dummy = prep(trucks_dummy, trucks) 

trucks_cleaned = bake(trucks_dummy, trucks) 
```

Task 3:  
```{r task 3}
set.seed(64)
clusters = kmeans(trucks_cleaned, 2)
```

```{r}
trucks = augment(clusters, trucks)
str(trucks)
```


```{r}
ggplot(trucks, aes(x=Distance,y=Speeding,color=factor(.cluster))) + geom_point() 
```

The clusters are similar to what I assumed from the first graph, with the exception of 1 driver above 100 miles who was clustered with the <100 miles/day group.  

Task 4:  
```{r task 4}
set.seed(412)
clusts = 
  tibble(k = 1:8) %>%
  mutate(
    kclust = map(k, ~kmeans(trucks_cleaned, .x)),
    tidied = map(kclust, tidy),
    glanced = map(kclust, glance),
    augmented = map(kclust, augment, trucks_cleaned)
  )

clusters = 
  clusts %>%
  unnest(cols = c(tidied))

assignments = 
  clusts %>% 
  unnest(cols = c(augmented))

clusterings = 
  clusts %>%
  unnest(cols = c(glanced))


ggplot(assignments, aes(x = Distance, y = Speeding)) +
  geom_point(aes(color = .cluster), alpha = 0.8) + 
  facet_wrap(~ k)
```

3 or 4 clusters seems to be most appropriate and allows the drivers to be clustered by speeders vs. non-speeders (3 clusters) or clustered by speeders and distance (4 clusters).    

Task 5:
```{r task 5}
ggplot(clusterings, aes(k, tot.withinss)) +
  geom_line() +
  geom_point() + theme_bw()
```

4 seems to be the best value for k.  

Task 6:
```{r task 6}
set.seed(64)
clusters = kmeans(trucks_cleaned, 4)
```

```{r}
trucks = augment(clusters, trucks)
str(trucks)
```

```{r}
ggplot(trucks, aes(x=Distance,y=Speeding,color=factor(.cluster))) + geom_point() 
```

4 clusters groups the drivers into:  
1) drivers who drive under 100 miles/day and speed < ~15%  
2) drivers who drive under 100 miles/day and speed > ~15%  
3) drivers who drive over 100 miles/day and speed < ~35%  
4) drivers who drive over 100 miles/day and speed > ~35%     

